### 2023-03-08 README.Rmd

To obtain the dependency graph of R packages, use `resolve`. Currently, this package supports both CRAN and Github packages.

```r
library(rang)
x <- resolve(pkgs = c("sna", "schochastics/rtoot"), snapshot_date = "2022-11-30")
```

>>>>

To obtain the dependency graph of R packages, use `resolve`. Currently, this package supports CRAN, Bioconductor, GitHub, and local packages.

```r
library(rang)
x <- resolve(pkgs = c("sna", "schochastics/rtoot", "S4Vectors"), snapshot_date = "2022-11-30")
```
